Bee brain size is positively associated with urban lifestyles but not with positive population trends

### 2022-11-17 Manuscript/Ms.Rmd
minor edit

Our study explores the long standing idea that species with higher encephalisation (i.e., large brain mass relative to their body) are more likely to thrive in urbanised areas. To investigate this, we have used a dataset of bees captured in North America and Europe with information about brain weight and body size. Then, we downloaded for all these species the occurrence information from the Global Biodiversity Information Facility (GBIF) and delimited two areas based on the states or countries with highest density of records. After curating the occurrence data to avoid possible biases, we extracted the land use classification

uses bee traits measured from North America and Europe to explore how different habitat types influence bee cognitive abilities measured as the deviation of the brain weight relative to their body size. To explore this, we first downloaded for our set of species, occurrence data from the Global Biodiversity Information Facility from North America and Europe. First, we identified the areas with highest density of occurrences and delimited based on that our study regions (East Coast of Unites States and North Central Europe). Second, we filtered the resulting occurrence records (e.g., we deleted duplicates and selected species with a homogeneous geographical distribution). Third, for the resulting species we extracted

>>>>

Our study explores the long standing idea that species with higher encephalisation (i.e., large brain mass relative to their body) are more likely to thrive in urbanised areas. To investigate this, we have used a dataset of bees captured in North America and Europe with information about brain weight and body size. Then, we downloaded for all these species the occurrence information from the Global Biodiversity Information Facility (GBIF) and delimited two areas based on the states or countries with highest density of records. After curating the occurrence data to avoid possible biases, we extracted the land use classification for each of the records and summarised the most representative classifications into 3 different categories: natural, agricultural and urban.
